### 2015-12-13 Thesis Draft Tianpei Chen/Thesis Draft/C-CSVR.tex

The mathematical foundation of kernel based methods is RKHS which is defined in complex domain, however most of the practitioners are dealing with real data sets. In communication and signal processing area, the channel gains, signals, waveforms etc. are all represented in complex form. Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain. The results in\cite{bouboulis2013complex} demonstrate the better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernels.  
Based on this work, we derive a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR). The detector can work in two parallel real SVR channels which can be solved independently. Moreover, only the real part of kernel matrix is needed in both channels. This means a large amount of computation cost saving can be achieved.
Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
is constructed without offset, Therefore, for each real SVR without offset, 
%in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed. By this strategy, two variables can be updated at each iteration, with much smaller searching time.
Two types of combined single optimization variable selection strategy are proposed based on the work in \cite{steinwart2011training}. The proposed combined single optimization variable selection strategy can approximate optimal double optimization variable selection strategy. The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.
\section{Complex Support Vector Preliminary Detector}
\section{Channel Hardening Approximation}
\section{CSVPD-LAS versus MMSE-LAS}
The single solution based metaheuristics which are also defined as trajectory methods, start from an initial solution and the search process performs on a single solution at any time as a trajectory in the searching space. In resent years, several single solution based metaheuristic algorithms are applied to LS-MIMO detection problem, such as likelihood ascend searching (LAS) algorithm and variants\cite{vardhan2008low}\cite{cerato2009hardware}\cite{li2010multiple} and Tabu search algorithms and variants\cite{srinidhi2011layered}\cite{datta2010random}. 
\section{CSVPD-OPIC versus MMSE-OPIC}

>>>>

The mathematical foundation of kernel based methods is RKHS which is defined in complex domain, however most of the practitioners are dealing with real data sets. In communication and signal processing area, the channel gains, signals, waveforms etc. are all represented in complex form. Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain. The results in\cite{bouboulis2013complex} demonstrate the better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernels.  
Based on this work, we derive a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR). The detector can work in two parallel real SVR channels which can be solved independently. Moreover, only the real part of kernel matrix is needed in both channels. This means a large amount of computation cost saving can be achieved.
Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
is constructed without offset, Therefore, for each real SVR without offset, 
%in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed. By this strategy, two variables can be updated at each iteration, with much smaller searching time.
Two types of combined single optimization variable selection strategy are proposed based on the work in \cite{steinwart2011training}. The proposed combined single optimization variable selection strategy can approximate optimal double optimization variable selection strategy. The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.
\section{Complex Support Vector Preliminary Detector}
\section{Channel Hardening Approximation}
\section{SVPD-LAS versus MMSE-LAS}
The single solution based metaheuristics which are also defined as trajectory methods, start from an initial solution and the search process performs on a single solution at any time as a trajectory in the searching space. In resent years, several single solution based metaheuristic algorithms are applied to LS-MIMO detection problem, such as likelihood ascend searching (LAS) algorithm and variants\cite{vardhan2008low}\cite{cerato2009hardware}\cite{li2010multiple} and Tabu search algorithms and variants\cite{srinidhi2011layered}\cite{datta2010random}. Here we consider SVPD aided multi update- LAS algorithm (SVPD-MLAS), which utilizes SVPD to get the initial estimate of the transmit symbol vector, we compare its performance with MMSE aided multi-update LAS algorithm (MMSE-MLAS), simulation results demonstrate the performance improvement of SVPD-MLAS over MMSE-MLAS.
\section{CSVPD-OPIC versus MMSE-OPIC}
The Second post processing detector we consider is parallel interference cancellation (PIC). PIC works in a multi-stage manner, at the $l+1$th stage, PIC utilizes the decisions made for all the other users at $l$the stage to cancel the interference present in the received signal $\mathbf{y}$ for the desired substream. Comparing to successive interference cancellation (SIC), PIC has a lower processing delay and is more robust to inter stream error propagation\cite{chin2002parallel}. These two gains increase when the number of users increases. SVPD is used in the first stage of PIC algorithm, referred as SVPD-PIC, we compare the performance of SVPD-PIC with MMSE aided PIC (MMSE-PIC), and simulation results demonstrate a considerate performance improvement can be achieved in LS-MIMO systems.

Fig. \ref{PIC scheme}, shows the structure of PIC scheme. In the first stage , the initial estimate of transmit symbol vector $\mathbf{s}$ is generated by preliminary detectors (e.g., SVPD, ZF, MMSE). In the following stages, as oppose to SIC, that cancels the interference from one substream at each stage, PIC cancels all the interference from the previous decisions of other substreams except the desired substream to be refined. This interference cancellation (IC) process can be applied to all the substreams in parallel, thus the processing delay can be reduced. After several stages refinement, the final solution is got.

Let the superscript $l$ indexes the $l$th stage, the subscript $i$ indexes the $i$th substream and its residual observation after performing IC to received signal vector, $\mathbf{h}_{i}$ denotes the $i$th column of $\mathbf{H}$, corresponding to CSI of $i$th substream, at $l+1$ stage, the residual observation $\hat{\mathbf{y}}^{l+1}_{i}$ of the $i$th substream $\hat{\mathbf{s}}^{l+1}_{i}$ is given by
\begin{equation}
\mathbf{y}^{l+1}_{i}=\mathbf{y}-\sum_{m\neq i}^{N_{t}}\mathbf{h}_{m}\hat{\mathbf{s}}^{l}_{m}, \quad i=1,2,\ldots, N_{t} 
\label{residual observation}
\end{equation}

$\hat{\mathbf{s}}^{l+1}_{i}$ then is refined by residual  observation $\mathbf{y}^{l+1}_{i}$ and CSI $\mathbf{h}_{i}$, 
\begin{equation}
\hat{\mathbf{s}}^{l+1}_{i}=\arg\min_{\tilde{\mathbf{s}}_{i}}\in \mathbb{O}||\mathbf{y}^{l+1}_{i}-\mathbf{h}_{i}\tilde{\mathbf{s}}_{i}||^{2},
\label{refine PIC}
\end{equation}

(\ref{refine PIC}) can be performed by suboptimal detectors (e.g., SVPD, ZF, MMSE). In order to reduce the computational cost, the full residual observation $\mathbf{y}_{f}$ by cancelling the interference from all the substreams to the received signal vector is calculated first,
\begin{equation}
\mathbf{y}_{f}=\mathbf{y}-\sum_{m=1}^{N_{t}}\mathbf{h}_{m}\hat{\mathbf{s}}^{l}_{m},
\label{full residual observation}
\end{equation}  
then (\ref{residual observation}) can be rewritten as 
\begin{equation}
\mathbf{y}^{l+1}_{i}=\mathbf{y}_{f}+\mathbf{h}_{i}\hat{\mathbf{s}}^{l}_{i} \quad i=1,2,\ldots, N_{t},
\label{residual observation 2}
\end{equation}

### 2015-12-13 Thesis Draft Tianpei Chen/Thesis Draft/C-GA.tex

\chapter{Low Complexity Near Optimal Hybrid Detector based on Genetic Algorithm}\label{Chapter GA}
In the previous chapter, we introduce two CSVPD aided local search based algorithms, and show the improvement CSVD-LAS -OPIC comparing to MMSE-LAS -OPIC.    
a current trend is the hybridization of of single solution based metaheuristics algorithms in population-based ones, working as intelligent subordinate heuristic operators. In this chapter, we introduce Hybrid Genetic Algorithms which utilizes OPIC as a genetic operator and accelerate the revolution process comparing to random revolution. Furthermore, instead of randomly generated initial population, the solution of the CSVPD is fed to Hybrid GA and the initial generation consists of the neighbour of the initial solution from CSVPD.  
\section{CSVPD aided Hybrid Genetic Algorithm}
Genetic Algorithm (GA) is one of the population-based metaheuristic algorithms and can be viewed as a computational model of natural biological evolution process. GA works iteratively and in each iteration it handles a fixed size population of individuals. A number of intelligent genetic operators are used to update the population. Usually the individuals are a string of symbols that represent a candidate solution to the problems. GA has been applied in Code Division Multiple Access (CDMA) detection problem\cite{juntti1997genetic}\cite{ergun2000multiuser}.

Figure (\ref{}) shows the flow chart of the proposed hybrid GA. In the beginning, the initial solution of CSVPD is fed to GA, a initial population of solutions are generated based on this initial solution, then in each iteration, each candidate solution is evaluated and selected by the fitness function. The elites are selected as parents which can generate offspring. The offsprings are generated by recombining a pair of parents, this process is called crossover. Then mutation operates to offsprings with a given possibility. OPIC is integrated in GA as an operator that can accelerate the process that GA approximate to optimal solution. The populations is finally reconstructed by the parents and their offsprings. The best solution is chosen based on the fitness function when the stopping criteria satisfied.

\subsection{Initialization}
Let $\mathbb{P}_{i}$ denotes the $i$th generation set consists of $|\mathbb{P}|$ symbol vectors, which is fixed in different generations. The estimated symbol vector from SVPD serves as the generation seed for the initial generation. The initial generation is generated by flipping a fix number of symbols to the nearest point in the symbol constellation alphabet randomly.

@@

We now use a binary sequence generated by SVPD to illustrate how the flipping process works, let $b_{SVPD}\in \mathbb{B}^{N_{t}}, \mathbb{B}=[+1, -1], N_{t}=8$ denotes the the binary sequence generated by SVPD, 
\begin{equation}
b_{SVPD}=[1, -1, -1, 1, -1, 1, 1, -1],
\end{equation}  
$\mathcal{F}=1$, means there is one symbol difference between the original symbol vector and the objective symbol vector after flipping. Let $b_{1}, b_{2}, \ldots b_{|\mathbb{P}|-1}$ denotes the individuals in the initial generation which are generated by perturbing seed vector $b_{SVPD}$. Fig.\ref{random flipping} shows how this random flipping scheme works.
\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\include{randomFlipping.tex_pdf}
\caption{Random Flipping with $\mathcal{F}=1$}
\label{random fipping}
\end{figure}
The initial generation is $\mathbb{P}=[b_{SVPD}, b_{1}, b_{2}, \ldots b_{|\mathbb{P}|-1}$.
\subsection{Selection}
The individuals in each generation are evaluated by the fitness function. In LS-MIMO detection problem. Euclidean distance is used as the fitness function, given by 
\begin{equation}
f(\mathbf{s_{i}})=||\mathbf{y}-\mathbf{H}\mathbf{s}_{i}||^{2}, 
\label{fitness function}
\end{equation}
where $\mathbf{s}_{i}$ denotes the $i$th individual symbol vector in the generation, the individual with the smallest fitness function value is the fittest candidate (elite) in the generation.

In each generation, the individuals with small $f(\mathbf{s}_{i})$ are chosen as the parents to generate offsprings, the offsprings are generated by recombining the parent symbol vectors, this process is recombination or crossover. In crossover process, crossover point is randomly chosen in parent symbol vectors and the subpart of a pair of parent symbol vectors up to that crossover point are interchanged. A simple cased of this process is shown in Fig.\ref{crossover}.
\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\include{crossover.tex_pdf}
\caption{Crossover operation to a pair of parent binary sequence}
\label{crossover}
\end{figure}
\subsection{Mutation}
The GA in operates in a sub searching space, which is initially, determined by the $\mathcal{F}$ neighbourhood of the seed symbol vector. The major difficulties in the revolution process in the convergence to the local minima of the sub searching space. Mutation is a strategy that helps GA to escape from local minima. Mutations operates by randomly perturbation of a small number of coordinates in offspring symbol vectors with a small possibility defined by the users. Fig.\ref{mutation} shows how mutation works. 
\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\include{mutation.tex_pdf}
\caption{Mutation operation to one bit in binary sequence}
\label{mutaion}
\end{figure}
\subsection{OPIC} 
\subsection{Stopping Criteria}

>>>>

\chapter{Low Complexity Near Optimal Hybrid Detector based on Genetic Algorithm}\label{Chapter GA}
In the previous chapter, we introduce two CSVPD aided local search based algorithms, and show the improvement CSVD-LAS -OPIC comparing to MMSE-LAS -OPIC.    
a current trend is the hybridization of of single solution based metaheuristics algorithms in population-based ones, working as intelligent subordinate heuristic operators. In this chapter, we introduce Hybrid Genetic Algorithms which utilizes OPIC as a genetic operator and accelerate the revolution process comparing to random revolution. Furthermore, instead of randomly generated initial population, the solution of the CSVPD is fed to Hybrid GA and the initial generation consists of the neighbour of the initial solution from CSVPD.  
\section{SVPD aided Hybrid Genetic Algorithm}
Genetic Algorithm (GA) is one of the population-based metaheuristic algorithms and can be viewed as a computational model of natural biological evolution process. GA works iteratively and in each iteration it handles a fixed size population of individuals. A number of intelligent genetic operators are used to update the population. Usually the individuals are a string of symbols that represent a candidate solution to the problems. GA has been applied in Code Division Multiple Access (CDMA) detection problem\cite{juntti1997genetic}\cite{ergun2000multiuser}.

Figure (\ref{}) shows the flow chart of the proposed hybrid GA. In the beginning, the initial solution of CSVPD is fed to GA, a initial population of solutions are generated based on this initial solution, then in each iteration, each candidate solution is evaluated and selected by the fitness function. The elites are selected as parents which can generate offspring. The offsprings are generated by recombining a pair of parents, this process is called crossover. Then mutation operates to offsprings with a given possibility. OPIC is integrated in GA as an operator that can accelerate the process that GA approximate to optimal solution. The populations is finally reconstructed by the parents and their offsprings. The best solution is chosen based on the fitness function when the stopping criteria satisfied.
\subsection{Initialization}
Let $\mathbb{P}_{i}$ denotes the $i$th generation set consists of $|\mathbb{P}|$ symbol vectors, which is fixed in different generations. The estimated symbol vector from SVPD serves as the generation seed for the initial generation. The initial generation is generated by flipping a fix number of symbols to the nearest point in the symbol constellation alphabet randomly.

@@

We now use a binary sequence generated by SVPD to illustrate how the flipping process works, let $b_{SVPD}\in \mathbb{B}^{N_{t}}, \mathbb{B}=[+1, -1], N_{t}=8$ denotes the the binary sequence generated by SVPD, 
\begin{equation}
b_{SVPD}=[1, -1, -1, 1, -1, 1, 1, -1],
\end{equation}  
$\mathcal{F}=1$, means there is one symbol difference between the original symbol vector and the objective symbol vector after flipping. Let $b_{1}, b_{2}, \ldots b_{|\mathbb{P}|-1}$ denotes the individuals in the initial generation which are generated by perturbing seed vector $b_{SVPD}$. Fig.\ref{random flipping} shows how this random flipping scheme works.
\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\input{randomFlipping.pdf_tex}
\caption{Random Flipping with $\mathcal{F}=1$}
\label{random fipping}
\end{figure}
The initial generation is $\mathbb{P}=[b_{SVPD}, b_{1}, b_{2}, \ldots b_{|\mathbb{P}|-1}$.
\subsection{Selection}
The individuals in each generation are evaluated by the fitness function. In LS-MIMO detection problem. Euclidean distance is used as the fitness function, given by 
\begin{equation}
f(\mathbf{s_{i}})=||\mathbf{y}-\mathbf{H}\mathbf{s}_{i}||^{2}, 
\label{fitness function}
\end{equation}
where $\mathbf{s}_{i}$ denotes the $i$th individual symbol vector in the generation, the individual with the smallest fitness function value is the fittest candidate (elite) in the generation.
In each generation, the individuals with small $f(\mathbf{s}_{i})$ are chosen as the parents to generate offsprings, the offsprings are generated by recombining the parent symbol vectors, this process is recombination or crossover. In crossover process, crossover point is randomly chosen in parent symbol vectors and the subpart of a pair of parent symbol vectors up to that crossover point are interchanged. A simple cased of this process is shown in Fig.\ref{crossover}.

\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\input{crossover.pdf_tex}
\caption{Crossover operation to a pair of parent binary sequence}
\label{crossover}
\end{figure}

\subsection{Mutation}
The GA in operates in a sub searching space, which is initially, determined by the $\mathcal{F}$ neighbourhood of the seed symbol vector. The major difficulties in the revolution process in the convergence to the local minima of the sub searching space. Mutation is a strategy that helps GA to escape from local minima. Mutations operates by randomly perturbation of a small number of coordinates in offspring symbol vectors with a small possibility defined by the users. Fig.\ref{mutation} shows how mutation works. 
\iffalse
\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\input{mutation.pdf_tex}
\caption{Mutation operation to one bit in binary sequence}
\label{mutaion}
\end{figure}
\fi

\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\input{mutation.pdf_tex}
\caption{Mutation operation to one bit in binary sequence}
\label{mutation}
\end{figure}

\subsection{OPIC} 
\subsection{Stopping Criteria}
